The limits of self commitment and private paternalism \thanks{}

### 2022-07-15 OA.tex
change scheme in figures
tot vs tut inference analysis

\begin{figure}[H]
        \caption{Empirical CDF of APR: fee-focing vs status-quo}
    \label{ecdf_fc}
    \begin{center}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/cdf_eff_pro_2.pdf}
    \end{center}
    \scriptsize This figure plots the empirical cumulative distribution of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The doted line at the bottom is the difference of the status-quo CDF minus the fee-forcing CDF. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
    % \texttt{ecdf\_fc.do}}
\end{figure}

@@

\scriptsize {
\noindent This figure reports bivariate regressions of the form $\widehat{TakeUp} = \alpha + \beta \: X_i + \epsilon_i$, where $\widehat{TakeUp}$ is the prediction using random forests. The figure reports the $\beta$ coefficients for different $X_i$'s along with 95\% confidence intervals. Panel (a) focuses on take up in the arm where clients could chose among the fee-commitment contract and the status quo contract. Panel (b) focuses on the arm where clients could chose among the promise-commitment contract and the status quo contract. Using random forests we can predict who takes up the fee-forcing contract with 85\% accuracy out of sample.\footnote{Correcting for the fact that most chose the status-quo contract using the method of SMOTE, \cite{smote} we find an accuracy rate of 75\%.} Which suggests that choice among contracts is not purely random. This figure shows that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and those that ask for a remainder of their due payments (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice. The opposite holds for clients that are more economically vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.
}

@@

\vspace{.2in}
\normalsize
\linespread{1.25}

@@

\subsubsection{LATE: ToT \& TuT}
\vspace{.2in}
\normalsize
\linespread{1.25}

@@

\begin{table}[H]
\caption{Effect of frequent payment in observational data}
\label{attrition_table}
\begin{center}
\scriptsize{\input{./Tables/def_te_obs.tex}}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{def\_te\_obs.do}
\end{table}

>>>>

\begin{figure}[H]
        \caption{Empirical CDF of APR: fee-focing vs status-quo}
    \label{ecdf_fc}
    \begin{center}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/cdf_eff_pro_2.pdf}
    \end{center}
    \scriptsize This figure plots the empirical cumulative distribution of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The doted line at the bottom is the difference of the status-quo CDF minus the fee-forcing CDF. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
    % \texttt{ecdf\_eff.do}}
\end{figure}

@@

\scriptsize 
\noindent This figure reports bivariate regressions of the form $\widehat{TakeUp} = \alpha + \beta \: X_i + \epsilon_i$, where $\widehat{TakeUp}$ is the prediction using random forests. The figure reports the $\beta$ coefficients for different $X_i$'s along with 95\% confidence intervals. Panel (a) focuses on take up in the arm where clients could chose among the fee-commitment contract and the status quo contract. Panel (b) focuses on the arm where clients could chose among the promise-commitment contract and the status quo contract. Using random forests we can predict who takes up the fee-forcing contract with 85\% accuracy out of sample.\footnote{Correcting for the fact that most chose the status-quo contract using the method of SMOTE, \cite{smote} we find an accuracy rate of 75\%.} Which suggests that choice among contracts is not purely random. This figure shows that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and those that ask for a remainder of their due payments (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice. The opposite holds for clients that are more economically vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.

\subsection{Bounding ToT \& TuT} \label{bound_tot_tut_appendix}

\vspace{.2in}
\normalsize
\linespread{1.25}
%Really force it to normal size and linespread
\normalsize
\linespread{1.25}

Even without the exclusion restriction, it’s possible to bound $\mathbb{E}[Y_1-Y_0\;|\;T=0]$ and $\mathbb{E}[Y_1-Y_0\;|\;T=1]$ using observed outcomes in the forced arm and observed take-up in the choice arm. It should also be possible to create bounds conditional on covariates. The basic approach is similar to that of \cite{huber_mellace}. \\

From the $Z=0$ arm we identify the distribution $F_0$ of $Y_0$, the potential outcome when forced into the no-commitment contract. Now, from the choice arm we know that around 90\% of people are $T=0$ types. Because choice was randomly assigned, the 90\% figure holds for all arms in the experiment. This tells us that $F_0$ is a 90\%-10\% mixture of $Y_0\;|\;T=0$ and $Y_0\;|\;T=1$. Cut out the bottom 10\% of $F_0$ and calculate the mean of this new distribution. Then cut out the top 10\% of $F_0$ and compute the mean of this new distribution. The result is an upper and lower bound for $\mathbb{E}[Y_0\;|\;T=0]$ that does not rely on the exclusion restriction. We can apply similar reasoning to bound $\mathbb{E}[Y_1\;|\;T=0]$ Combining the previous bounds gives a bound for the TuT that does not rely on the exclusion restriction, and analogous we can bound the ToT. \\

The \cite{huber_mellace} bounds for the ToT \& TuT APR are respectively:
\[\text{ToT} : [-481.8, 483.7]\quad\quad\quad\text{TuT} : [-17.9, 90.6]\]

Note that since both TuT and ToT estimates from the LATE approach lies inside these bounds, we do not falsify the exclusion restriction.

@@

\vspace{.2in}
\normalsize
\linespread{1.25}
%Really force it to normal size and linespread
\normalsize
\linespread{1.25}

@@

\subsubsection{LATE: ToT \& TuT}
\vspace{.2in}
\normalsize
\linespread{1.25}
%Really force it to normal size and linespread
\normalsize
\linespread{1.25}

@@

\begin{table}[H]
\caption{Effect of frequent payment in observational data}
\label{te_obs}
\begin{center}
\scriptsize{\input{./Tables/def_te_obs.tex}}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{def\_te\_obs.do}
\end{table}
